### 2017-08-27 comentarios-tesis/lecturadetesis18-09/20161019_Paola_Chapter_3_Part_A.tex
last changes to chapter 3

\documentclass[12pt,reqno]{amsart}
\usepackage{amsfonts,amssymb,amsmath,amsthm,mathrsfs,
            amsopn,amsxtra,amstext,amsbsy}
\usepackage{epsfig}
\usepackage{array}
\usepackage{url}
\usepackage{tikz}
%% \usepackage[spanish]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{hyperref,wasysym}
\usepackage{xcolor}
\usepackage{lipsum}
\usepackage{enumerate}
\usepackage{enumitem}% http://ctan.org/pkg/enumitem
\usepackage{verbatim}

\voffset=-10mm
\oddsidemargin=0pt
\evensidemargin=0pt
\topmargin=-10mm
\headsep=18pt
\headheight=18pt
\footskip=30pt
\topskip=0mm
\textwidth 167mm
\textheight=230mm
\parindent=0em
\marginparsep=0mm
\marginparwidth=0mm
\vfuzz2pt % Don't report over-full v-boxes if over-edge is small
\hfuzz6pt % Don't report over-full h-boxes if over-edge is small

% \newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{definicion}{Definición}
% \newtheorem{theorem}{Theorem}%[section]
% \newtheorem{lemma}[theorem]{Lemma}
% \newtheorem{corollary}[theorem]{Corollary}
% \newtheorem{conjecture}[theorem]{Conjecture}
% \theoremstyle{definition}
% \newtheorem{definition}[theorem]{Definition}
% \newtheorem{example}[theorem]{Example}
% \newtheorem{xca}[theorem]{Exercise}
% \theoremstyle{remark}
% \newtheorem{remark}[theorem]{Remark}
% \numberwithin{equation}{section}

% \def\phi{\varphi}
% \def\epsilon{\varepsilon}
\def\RE{\mbox{\rm Re}\,}
\def\IM{\mbox{\rm Im}\,}
% \def\AZ{|z|}
\newcommand{\rectangle}{\fboxsep0pt\fbox{\rule{0.3em}{0pt}\rule{0pt}{1.5ex}}}

%-------------------------mathcal

\def\A{{\mathcal A }}
\def\CC{{\mathcal C }}
\def\CH{{\mathcal H }}
\def\CK{{\mathcal K }}
\def\CM{{\mathcal M }}
\def\CP{{\mathcal P }}
\def\CS{{\mathcal S }}
\def\CR{{\mathcal R}}
\def\CRu{{\mathcal R}^{\rm u}}
\def\CT{{\mathcal T}}
\def\CTT{\widetilde{{\mathcal T}}}
\def\CW{{\mathcal W}}
\def\Li{{\mbox{\rm Li}}}
\def\WO{{\mathcal W}_{\Omega }}

%-------------------------------Bbb
\def\K{{\mathbb K }}
\def\C{{\mathbb C }}
\def\N{{\mathbb N }}
\def\NO{{\mathbb{N}_0 }}
\def\Z{{\mathbb Z }}
\def\R{{\mathbb R }}
\def\U{{\mathbb U }}
\def\D{{\mathbb D }}
%----------------------------Zusammengesetztes

\def\DB{\overline{\D}}
\def\Db#1{\overline{\D_{#1}}}
\def\DBR{\overline{\D_\rho}}
\def\DV{de la Vall\'ee Poussin }
\def\d#1{\D_{#1}}
\def\H{{\mathcal H}(\D)}
\def\Hb{{\mathcal H}(\DB)}
\def\HO{{\mathcal H}_0(\D )}
\def\Hoo#1{{\mathcal H}(\overline{\D_{#1}})}
\def\HB#1{{\mathcal H}(\D_{#1})}
\def\Ho#1{{\mathcal H}({#1})}
\def\Hyp{{}_2F_1}

\def\achtung#1{\alert{#1}}
\def\blue#1{{\color{blue} #1}}
\def\green#1{{\color{green} #1}}
\def\red#1{{\color{red} #1}}

\def\pick{{\mathscr P}}
\def\logpick{{\text{log}\,{\mathscr P}}}
\def\stammpick{\pick_{\!\!\!\raisebox{-2pt}{\scalebox{0.5}{$\int$}}}}
\def\stammpickpick{\stammpick\cap\pick}
\def\stammpicklogpick{\stammpick\cap\logpick}
\def\expstammpicklogpick{e^{\stammpicklogpick}}

%-------------------------Bakan-Ruscheweyh-Salinas 2015
\def\mid{\;:\ }
\def\hol#1{\text{Hol}(#1)}
\def\normhol#1#2{\text{Hol}_{#1}(#2)}

\DeclareMathOperator*{\cosig}{cosig}
\DeclareMathOperator*{\supp}{supp}

%graficos
%\pgfdeclareimage[width=5cm, height=3cm ]{recursiva}{./Png/recursiva.png}
%\pgfdeclareimage[width=5cm, height=5cm ]{alan}{./Png/Turing.jpeg}
%\pgfdeclareimage[width=5cm, height=5cm ]{programa}{./Png/maquina.png}
%\pgfuseimage{lala}

\renewcommand{\restriction}{\mathord{|}}

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup }

\title[Paola's Thesis Comments]{Paola's Thesis Comments}

\author[L. Salinas]{Luis Salinas}

\address{CCTVal and Departamento de Inform\'atica, UTFSM, Valpara\'\i so;
         \newline
         Mathematisches Institut, Universit\"at W\"urzburg;
         \newline
         \today} % October 06, 2016}

\email{luis.salinas@usm.cl}

\begin{document}

\maketitle%

\section{Chapter 3: Machine Learning Models.}

\def\myitem#1{ \item[\blue{\bf #1}] }

@@

\begin{thebibliography}{99}
\bibitem{Arce-2016}
Paola Arce, 
{\em Online Learning Method for Financial Time Series Forecasting\/}.
Dissertation, UTFSM, June 2016.

\end{thebibliography}

\end{document}

>>>>

%% \documentclass[12pt,reqno]{amsart}
%% \usepackage{amsfonts,amssymb,amsmath,amsthm,mathrsfs,
%%             amsopn,amsxtra,amstext,amsbsy}
%% \usepackage{epsfig}
%% \usepackage{array}
%% \usepackage{url}
%% \usepackage{tikz}
%% %% \usepackage[spanish]{babel}
%% \usepackage[utf8x]{inputenc}
%% \usepackage{fancyhdr}
%% \usepackage{graphicx}
%% \usepackage{hyperref,wasysym}
%% \usepackage{xcolor}
%% \usepackage{lipsum}
%% \usepackage{enumerate}
%% \usepackage{enumitem}% http://ctan.org/pkg/enumitem
%% \usepackage{verbatim}

%% \voffset=-10mm
%% \oddsidemargin=0pt
%% \evensidemargin=0pt
%% \topmargin=-10mm
%% \headsep=18pt
%% \headheight=18pt
%% \footskip=30pt
%% \topskip=0mm
%% \textwidth 167mm
%% \textheight=230mm
%% \parindent=0em
%% \marginparsep=0mm
%% \marginparwidth=0mm
%% \vfuzz2pt % Don't report over-full v-boxes if over-edge is small
%% \hfuzz6pt % Don't report over-full h-boxes if over-edge is small

%% % \newtheorem{conjecture}[theorem]{Conjecture}
%% \newtheorem{definicion}{Definición}
%% % \newtheorem{theorem}{Theorem}%[section]
%% % \newtheorem{lemma}[theorem]{Lemma}
%% % \newtheorem{corollary}[theorem]{Corollary}
%% % \newtheorem{conjecture}[theorem]{Conjecture}
%% % \theoremstyle{definition}
%% % \newtheorem{definition}[theorem]{Definition}
%% % \newtheorem{example}[theorem]{Example}
%% % \newtheorem{xca}[theorem]{Exercise}
%% % \theoremstyle{remark}
%% % \newtheorem{remark}[theorem]{Remark}
%% % \numberwithin{equation}{section}

%% % \def\phi{\varphi}
%% % \def\epsilon{\varepsilon}
%% \def\RE{\mbox{\rm Re}\,}
%% \def\IM{\mbox{\rm Im}\,}
%% % \def\AZ{|z|}
%% \newcommand{\rectangle}{\fboxsep0pt\fbox{\rule{0.3em}{0pt}\rule{0pt}{1.5ex}}}

%% %-------------------------mathcal

%% \def\A{{\mathcal A }}
%% \def\CC{{\mathcal C }}
%% \def\CH{{\mathcal H }}
%% \def\CK{{\mathcal K }}
%% \def\CM{{\mathcal M }}
%% \def\CP{{\mathcal P }}
%% \def\CS{{\mathcal S }}
%% \def\CR{{\mathcal R}}
%% \def\CRu{{\mathcal R}^{\rm u}}
%% \def\CT{{\mathcal T}}
%% \def\CTT{\widetilde{{\mathcal T}}}
%% \def\CW{{\mathcal W}}
%% \def\Li{{\mbox{\rm Li}}}
%% \def\WO{{\mathcal W}_{\Omega }}

%% %-------------------------------Bbb
%% \def\K{{\mathbb K }}
%% \def\C{{\mathbb C }}
%% \def\N{{\mathbb N }}
%% \def\NO{{\mathbb{N}_0 }}
%% \def\Z{{\mathbb Z }}
%% \def\R{{\mathbb R }}
%% \def\U{{\mathbb U }}
%% \def\D{{\mathbb D }}
%% %----------------------------Zusammengesetztes

%% \def\DB{\overline{\D}}
%% \def\Db#1{\overline{\D_{#1}}}
%% \def\DBR{\overline{\D_\rho}}
%% \def\DV{de la Vall\'ee Poussin }
%% \def\d#1{\D_{#1}}
%% \def\H{{\mathcal H}(\D)}
%% \def\Hb{{\mathcal H}(\DB)}
%% \def\HO{{\mathcal H}_0(\D )}
%% \def\Hoo#1{{\mathcal H}(\overline{\D_{#1}})}
%% \def\HB#1{{\mathcal H}(\D_{#1})}
%% \def\Ho#1{{\mathcal H}({#1})}
%% \def\Hyp{{}_2F_1}

%% \def\achtung#1{\alert{#1}}
%% \def\blue#1{{\color{blue} #1}}
%% \def\green#1{{\color{green} #1}}
%% \def\red#1{{\color{red} #1}}

%% \def\pick{{\mathscr P}}
%% \def\logpick{{\text{log}\,{\mathscr P}}}
%% \def\stammpick{\pick_{\!\!\!\raisebox{-2pt}{\scalebox{0.5}{$\int$}}}}
%% \def\stammpickpick{\stammpick\cap\pick}
%% \def\stammpicklogpick{\stammpick\cap\logpick}
%% \def\expstammpicklogpick{e^{\stammpicklogpick}}

%% %-------------------------Bakan-Ruscheweyh-Salinas 2015
%% \def\mid{\;:\ }
%% \def\hol#1{\text{Hol}(#1)}
%% \def\normhol#1#2{\text{Hol}_{#1}(#2)}

%% \DeclareMathOperator*{\cosig}{cosig}
%% \DeclareMathOperator*{\supp}{supp}

%% %graficos
%% %\pgfdeclareimage[width=5cm, height=3cm ]{recursiva}{./Png/recursiva.png}
%% %\pgfdeclareimage[width=5cm, height=5cm ]{alan}{./Png/Turing.jpeg}
%% %\pgfdeclareimage[width=5cm, height=5cm ]{programa}{./Png/maquina.png}
%% %\pgfuseimage{lala}

%% \renewcommand{\restriction}{\mathord{|}}

%% \newcommand\blfootnote[1]{%
%%   \begingroup
%%   \renewcommand\thefootnote{}\footnote{#1}%
%%   \addtocounter{footnote}{-1}%
%%   \endgroup }

%% \title[Paola's Thesis Comments]{Paola's Thesis Comments}

%% \author[L. Salinas]{Luis Salinas}

%% \address{CCTVal and Departamento de Inform\'atica, UTFSM, Valpara\'\i so;
%%          \newline
%%          Mathematisches Institut, Universit\"at W\"urzburg;
%%          \newline
%%          \today} % October 06, 2016}

%% \email{luis.salinas@usm.cl}

%% \begin{document}

%% \maketitle%

%% \section{Chapter 3: Machine Learning Models.}

%% \def\myitem#1{ \item[\blue{\bf #1}] }

\section{Chapter 3: REMARKS FROM 20161019}

@@

%% \end{document}

### 2017-08-27 src/4_OnlineLearning.tex
last changes to chapter 3

\begin{figure}[!h]
  \centering
  \includegraphics[width=0.8\textwidth]{img/VCdimension}
  \caption{VC dimension example from \cite{vapnik2013nature}. The left figure
  shows that the 3 dichotomies can be shattered by a line in a plane. However, if we
  add an extra vector $z_4$, it is impossible to shatter them with a
  line. Therefore, linear classifiers has VC dimension equals to $d+1$ where $d$
  is the dimension of the instance space $X$.}
  \label{fig:vcdimension}
\end{figure}

@@

The relationship between generalisation error and the amount of training or
input data is intuitive: the more data is given to the learning model $f$, the
more evidence the algorithm has about the problem. In the limit, the input data
will contain every possible example, so the algorithm will generalize perfectly.
However, for some $f \in H$, the best hypothesis $\hat{f}$ might be far away to
the best hypothesis class but it is the best that all the learners can hope.
Therefore, to choose the right hypothesis class $H$ is crucial. The error of
this best hypothesis is formalised as the {\em approximation or generalisation
error} \cite{niyogi1996relationship}.

@@

The relationship between the generalisation error and the hypothesis complexity
is less intuitive. If the class $H$ complexity (VC dimension) increases, then to
mantain an {\em estimation error}, the {\em sample complexity} increases.
Therefore, if we have a low complex model we will reduce the {\em sample complexity}
but it will increase {\em generalisation error}. The hypothesis has to be
sufficiently complex to capture the characteristics of the data.

>>>>

\begin{figure}[!h]
  \centering
  \includegraphics[width=0.8\textwidth]{img/VCdimension}
  \caption{VC dimension example from \cite{vapnik2013nature}. The example shows 2-dimensional vectors $z_k=(x_k,y_k)$,  $k=1,2,3,4$. The left figure
  shows that the 3 dichotomies can be shattered by a line in a plane. However, if we
  add an extra vector $z_4$, it is impossible to shatter them with a
  line. Therefore, linear classifiers has VC dimension equals to $d+1$ where $d$
  is the dimension of the instance space $X$.}
  \label{fig:vcdimension}
\end{figure}

@@

The relationship between generalisation error and the amount of training or
input data is intuitive: the more data is given to the learning model $f$, the
more evidence the algorithm has about the problem. In the limit, the input data
will contain every possible example, so the algorithm will generalize perfectly.
However, for some $f \in \mathscr{H}$, the best hypothesis $\hat{f}$ might be far away to
the best hypothesis class but it is the best that all the learners can hope.
Therefore, to choose the right hypothesis class $\mathscr{H}$ is crucial. The error of
this best hypothesis is formalised as the {\em approximation or generalisation
error} \cite{niyogi1996relationship}.

@@

The relationship between the generalisation error and the hypothesis complexity
is less intuitive. If the class $\mathscr{H}$ complexity (VC dimension) increases, then to
mantain an {\em estimation error}, the {\em sample complexity} increases.
Therefore, if we have a low complex model we will reduce the {\em sample complexity}
but it will increase {\em generalisation error}. The hypothesis has to be
sufficiently complex to capture the characteristics of the data.
